%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,10.9pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[a4paper, top=0.5cm, bottom=0.5cm, left=1.5cm, right=1.5cm]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centred version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Morgan Thomas} \\[7.5pt]
\href{https://github.com/emtee14}{\raisebox{-0.05\height}\faGithub\ emtee14} \ $|$ \ 
\href{https://linkedin.com/in/morgan-thomas14}{\raisebox{-0.05\height}\faLinkedin\ morgan-thomas14} \ $|$ \ 
\href{https://morganthomas.uk}{\raisebox{-0.05\height}\faGlobe \ morganthomas.uk} \ $|$ \ 
\href{mailto:sc23mt2@leeds.ac.uk}{\raisebox{-0.05\height}\faEnvelope \ sc23mt2@leeds.ac.uk}  \\ 
\href{tel:+447853983405}{\raisebox{-0.05\height}\faMobile \ +44 7853 983405} \\
\end{tabularx}
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2023 -- 2026 & BSc Computer Science at \textbf{University of Leeds} \hfill \normalsize  \\
2021 -- 2023 & A-Levels at \textbf{Christleton High School} in Maths, Computer Science, and Physics \hfill (A,A,B) \\ 
& Extended Project Qualification - Developing a Crypto Currency (A*) \\
\end{tabularx}
%Experience
\section{Experience}
\begin{joblong}{Head of the Gryphon Project - Leeds University Rocketry Association}{Mar 2025 -- present}
    \item Leading a 25+ person engineering team to develop one of the UK's first student liquid rockets, having led the UK’s largest non-commercial rocket launch in June 2025.
    \item Authoring and reviewing technical documentation, performing design reviews, and implementing system-level requirements to ensure mission and safety compliance.
    \item Oversee a £15,000+ budget of university grants and partner donations across five sub-teams, managing procurement and manufacturing processes
\end{joblong}
\begin{joblong}{Flight Dynamics Lead - Leeds University Rocketry Association}{Sept 2024 -- Mar 2025}
    \item Produced and managed the UK’s first student safety case for a Large Rocket Permission submitted to the Civil Aviation Authority.
    \item Developed a simulation system using RocketPy to determine optimal launch windows and evaluate go/no-go from a custom weather metric generated using GFS and ECMWF forecasts.
    \item Added MPI parallelisation to RocketPy’s Monte Carlo simulations, enabling execution of 250,000 runs on the University’s HPC cluster.
    \item Automated parametric studies in RasAero II, optimising the rocket to achieve speeds of Mach 3.5 with an apogee of 160,000ft.
\end{joblong}
%Projects
\section{Projects}
\begin{joblong}{Detection and Tracking using Motion Extraction and Voxel Projection}{Ongoing}
    \item Designing and implementing a distributed camera network to detect, track, and identify low-observable aerial objects beyond radar visibility.
    \item Developing a near real-time detection pipeline to aggregate sensor streams, performing tracking and state estimation.
    \item Implementing a sharded processing architecture to enable scalable real-time analysis across large geographic areas.
    \item Optimising the detection algorithm using simulated data from programmatically rendered scenes in Blender.
\end{joblong}
\begin{joblong}{XRTS - Flight and Trajectory Simulator}{\href{https://github.com/emtee14/xrts}{GitHub}}
    \item Developed a 6-degree-of-freedom trajectory simulator in Rust for rocket flight and recovery.
    \item Integrated with data produced from existing simulation software to simulate flights up to Mach 25.
    \item Added functionality to integrate with weather forecasting systems to simulate flight paths and determine landing areas.
\end{joblong}
\begin{joblong}{House Stats - Full-Stack Data Analytics Platform for the UK Housing Market}{\href{https://github.com/House-Stats}{GitHub}}
    \item Designed and built a web-based analytics platform for visualising and analysing UK Land Registry housing data.
    \item Engineered a distributed data-processing pipeline using Celery, Polars, and PostgreSQL, enabling sub-second analysis across 26M+ rows.
    \item Deployed and maintained a fully self-hosted infrastructure using Proxmox VMs and Docker containers to run the web server, PostgreSQL database, Celery cluster, and Kafka, ensuring reliability and scalability.
    \item Built data-analysis methods to remove anomalies and compute year-on-year price changes, highlighting seasonal trends in UK house prices that short-term comparisons miss.
\end{joblong}

\section{Interests \& Skills}
\centering
\begin{tabularx}{0.85\linewidth}{c c c c}
    Python &  Rust & Embedded Development & Physical Simulations (6-DoF, CFD) \\
    C  &  Java & Linux Administration & Classic Car Restoration \\
    Javascript & Web Development & Cycling & Rocketry \\
\end{tabularx}

\end{document}